Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-28 paper/evaluation.tex
more edits. bring back conclusion
label images, and change image placement for space

@@

\begin{figure}[t!]
  \centering
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
  \end{minipage}
  \quad
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
  \end{minipage}
  \caption{Compilation times.}
  \label{fig:compilation-times}
\end{figure}

\begin{figure}[t!]
  \centering
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
  \end{minipage}
  \quad
  \begin{minipage}[b]{0.45\linewidth}
    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
  \end{minipage}
  \caption{Configuration minimization.}
  \label{fig:config-minimization}
\end{figure}

@@

For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh. We explore different mesh sizes and randomly map neighboring networks to routers.

@@

@@

The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation. 
%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans. 
Figure~\ref{fig:config-minimization} shows the effect of minimization for the data center and backbone policies. In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.

>>>>

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
  \label{fig:compilation-times}
  \caption{Compilation time.}
\end{figure}

@@

%\begin{figure}[t!]
%  \centering
%  \begin{minipage}[b]{0.45\linewidth}
%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-dc.png}
%  \end{minipage}
%  \quad
%  \begin{minipage}[b]{0.45\linewidth}
%    \includegraphics[width=1.1\columnwidth]{figures/compilation-times-backbone.png}
%  \end{minipage}
%  \caption{Compilation times.}
%  \label{fig:compilation-times}
%\end{figure}

%\begin{figure}[t!]
%  \centering
%  \begin{minipage}[b]{0.45\linewidth}
%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-dc.png}
%  \end{minipage}
%  \quad
%  \begin{minipage}[b]{0.45\linewidth}
%    \includegraphics[width=1.1\columnwidth]{figures/config-compression-backbone.png}
%  \end{minipage}
%  \caption{Configuration minimization.}
%  \label{fig:config-minimization}
%\end{figure}

@@

For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh. We explore different mesh sizes and randomly map neighboring networks to routers. Even though each border router connects to many external peers, we count only the internal topology size.

@@

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
  \label{fig:config-min}
  \caption{Configuration minimization.}
\end{figure}

@@

The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation. 
%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans. 
Figure~\ref{fig:config-min} shows the effect of minimization for the data center and backbone policies. In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.
